### 2013-02-15 MSteenhagen-CV.tex
Created (and moved) professional organitions section

\ind Editor, \href{http://www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics}}

\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}

@@

\ind 2011. ``Seeing what another would.'' Utrecht University, \emph{Expert Meeting on Philosophical Aesthetics}.

\ind 2011. ``Representing the Trinity.'' University of Ghent, Annual conference of the Dutch Society of Aesthetics.

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% 
% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip

>>>>

@@

\ind 2011. ``Seeing what another would.'' Utrecht University, \emph{Expert Meeting on Aesthetics}.

\ind 2011. ``Representing the Trinity.'' University of Ghent, NGE Annual conference .

@@

% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% 
% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
% 
% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
% 
% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
% 
% \bigskip
\marginhead{Professional organisations}
\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}

\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{British Society of Aesthetics}
